\documentclass{beamer}
\usetheme{Madrid}
\usecolortheme{dolphin}
\definecolor{charcoal}{RGB}{54,69,79}
\setbeamercolor{structure}{fg=charcoal}
\setbeamercolor{palette primary}{bg=charcoal,fg=white}
\setbeamercolor{palette secondary}{bg=charcoal!90,fg=white}
\setbeamercolor{palette tertiary}{bg=charcoal!80,fg=white}
\setbeamercolor{palette quaternary}{bg=charcoal!70,fg=white}
\setbeamercolor{frametitle}{bg=charcoal,fg=white}
\setbeamercolor{title}{bg=charcoal,fg=white}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=2
}
\title[Sprint 3]{Game Project --- Sprint 3}
\subtitle{COP2250: Java Programming}
\author{Kevin Pyatt, Ph.D.}
\institute{State College of Florida \\ Pyatt Labs}
\date{Week 15}
\begin{document}
\begin{frame}
  \titlepage
\end{frame}
\begin{frame}{Sprint 3 --- Feature Complete}
\textbf{Last build sprint. By Thursday:}
\vspace{0.3cm}
\begin{tabular}{ll}
\toprule
\textbf{Requirement} & \textbf{Description} \\
\midrule
Invalid input handled & No crashes \\
Interface implemented & At least one \\
End condition functional & Game can end \\
Code commented & Every class and method \\
All OOP requirements met & See project overview \\
\bottomrule
\end{tabular}
\vspace{0.3cm}
\textit{Feature complete: a stranger compiles it, runs it, plays it without your help.}
\end{frame}
\begin{frame}{Sprint 3 Checklist}
\textbf{Run through before Thursday:}
\vspace{0.2cm}
\begin{itemize}
  \item \texttt{javac *.java} compiles with zero errors
  \item \texttt{java Main} launches the game
  \item Player completes at least one full game loop
  \item Invalid input does not crash the game
  \item End condition triggers correctly
  \item Every team member explains their assigned classes
\end{itemize}
\vspace{0.3cm}
\textit{If any item is unchecked, that is your work for today.}
\end{frame}
\begin{frame}[fragile]{Input Handling --- Required}
\begin{lstlisting}
while (running) {
    System.out.print("Enter command: ");
    try {
        String input = scanner.nextLine().trim();
        processCommand(input);
    } catch (Exception e) {
        System.out.println("Invalid input. Try again.");
    }
}
\end{lstlisting}
\vspace{0.3cm}
\textit{If your game crashes on bad input, it is not feature complete.}
\end{frame}
\begin{frame}{Code Quality}
\textbf{Every file must have:}
\vspace{0.2cm}
\begin{itemize}
  \item Header comment: class name, author, date, purpose
  \item Method comments: what it does, what it returns
  \item No dead code or commented-out blocks
  \item Meaningful variable names
\end{itemize}
\vspace{0.3cm}
\textit{During the defense I will read your code aloud.}\\
\textit{Write code you are willing to hear read back to you.}
\end{frame}
\begin{frame}{Today's Work}
\textbf{Use every minute:}
\vspace{0.2cm}
\begin{enumerate}
  \item Run the checklist --- fix what is failing
  \item Add comments to every class and method
  \item Test invalid input on every input point
  \item Confirm end condition triggers correctly
  \item Every team member runs the game solo --- no coaching
\end{enumerate}
\vspace{0.3cm}
\textbf{Thursday is Playtest.}\\
Another team compiles and runs your game cold.\\
\vspace{0.3cm}
\textit{It has to work without you explaining it.}
\end{frame}
\end{document}
