\documentclass{beamer}
\usetheme{Madrid}
\usecolortheme{dolphin}
\definecolor{charcoal}{RGB}{54,69,79}
\setbeamercolor{structure}{fg=charcoal}
\setbeamercolor{palette primary}{bg=charcoal,fg=white}
\setbeamercolor{palette secondary}{bg=charcoal!90,fg=white}
\setbeamercolor{palette tertiary}{bg=charcoal!80,fg=white}
\setbeamercolor{palette quaternary}{bg=charcoal!70,fg=white}
\setbeamercolor{frametitle}{bg=charcoal,fg=white}
\setbeamercolor{title}{bg=charcoal,fg=white}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=2
}
\title[Sprint 2 Check-In]{Game Project --- Sprint 2 Check-In}
\subtitle{COP2250: Java Programming}
\author{Kevin Pyatt, Ph.D.}
\institute{State College of Florida \\ Pyatt Labs}
\date{Week 14}
\begin{document}
\begin{frame}
  \titlepage
\end{frame}
\begin{frame}{Sprint 2 Requirements}
\textbf{Every team must show today:}
\vspace{0.3cm}
\begin{tabular}{ll}
\toprule
\textbf{Requirement} & \textbf{Evidence} \\
\midrule
Abstract class with 2+ subclasses & Show the files \\
At least one method override & Point to it in code \\
Composition relationship & Show the field \\
Core game loop functional & Run it live \\
\bottomrule
\end{tabular}
\vspace{0.3cm}
\textit{Compile and run in front of me. That is the only check that matters.}
\end{frame}
\begin{frame}{Demo Protocol}
\textbf{Each team in order:}
\vspace{0.2cm}
\begin{enumerate}
  \item Screen-share terminal
  \item \texttt{ls *.java} --- show all files
  \item \texttt{javac *.java} --- must compile clean
  \item \texttt{java Main} --- game runs and accepts input
  \item Explain abstract class and one subclass
\end{enumerate}
\vspace{0.3cm}
\textit{If the game loop is not functional, use remaining class time. Show me before you leave.}
\end{frame}
\begin{frame}{Apply This Week to Your Game}
\textbf{Abstract classes and interfaces belong in your game now.}
\vspace{0.3cm}
\begin{tabular}{lll}
\toprule
\textbf{Pattern} & \textbf{Example} & \textbf{Use} \\
\midrule
Abstract class & \texttt{Character} & Player, NPC share behavior \\
Interface & \texttt{Attackable} & Any class that can be hit \\
Interface & \texttt{Saveable} & Any class that persists state \\
\bottomrule
\end{tabular}
\vspace{0.3cm}
\textit{If your game has no interface yet, add one before Sprint 3.}
\end{frame}
\begin{frame}{Sprint 3 Preview}
\textbf{Feature complete by end of Week 15:}
\vspace{0.2cm}
\begin{itemize}
  \item All invalid input handled --- no crashes
  \item At least one interface implemented
  \item Win/lose/end condition functional
  \item Code organized and commented
  \item All OOP requirements met
\end{itemize}
\vspace{0.3cm}
\textbf{Playtest Thursday of Week 15.}\\
\textit{The clock is running. Get it working.}
\end{frame}
\begin{frame}{Individual Defense Preview}
\textbf{Week 16 --- you answer for your own code.}
\vspace{0.2cm}
\begin{itemize}
  \item Which classes did you write?
  \item Explain your abstract class
  \item Walk me through your game loop
  \item Where is exception handling?
  \item What would change with a GUI?
\end{itemize}
\vspace{0.3cm}
\textit{You cannot point to your teammate. You either know it or you do not.}\\
\vspace{0.3cm}
\textit{You built this. Own it.}
\end{frame}
\end{document}
